{{< var titll >}}

### 2024-07-13 presentation.qmd
abc
smallfix

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(huxtable)
library(kableExtra)
library(ManifoldDestiny)
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
appnf <- seloutput(selreport(basc))
appr1 <- seloutput(selreport(rigv[[1]]))
appr2 <- seloutput(selreport(rigv[[2]]))
appr3 <- seloutput(selreport(rigv[[3]]))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
cx
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
\end{equation*}

Election outome 
```{r, echo=F}
#pri_int_ex1
#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
#mean(app_ex1_cou$rdfc$alpha)
```

@@

$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$

Election outome
```{r, echo=F}
#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
#pos_int_ex1
```

@@

![](images/manifold.png){width=300}

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(huxtable)
library(kableExtra)
library(ManifoldDestiny)
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
appnf <- seloutput(rppnf <- selreport(basc))
appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r paste0(penf)`$
\end{equation*}

Election outome 
```{r, echo=F}
round(polynom::integral(penf,c(0,1)),3)
```

@@

$f(x)_{0}^{1}=`r paste0(per1)`$

Election outome
```{r, echo=F}
round(polynom::integral(per1,c(0,1)),3)
```

@@

The video "Conexiones Peligrosas"
